Genomic comparison

### 2021-10-07 analysis/OTT.Rmd
Add missing files
wflow_publish(files = list.files("analysis/", pattern = "*Rmd",     full.names = T))
wflow_publish(files = c("analysis/*"))

---
title: "R Notebook"
output: html_notebook
---

@@

```{r}
species <- c('Zostera marina', 'Zostera muelleri', 'Arabidopsis thaliana', 'Thellungiella parvula', 'Populus trichocarpa', 'Vitis vinifera', 'Amborella trichopoda', 'Oryza sativa', 'Zea mays', 'Brachypodium distachyon', 'Spirodela polyrhiza', 'Selaginella moellendorffi', 'Physcomitrella patens', 'Chlamydomonoas reinhardtii', 'Ostreococcus lucimarinus', 'Lemna gibba', 'Posidonia australis' ,'Amphibolis antarctica')
```

@@

```{r fig.width=14}
plot(ggdraw()+cowplot::draw_image('data/Species_timetree.svg'))
```

@@

```{r}
tree <- read.tree('data/timetree_species.nwk')
```

>>>>

---
title: "Phylogenetics"
output: html_notebook
---

@@

```{r}
species <- c('Zostera marina', 'Zostera muelleri', 'Arabidopsis thaliana', 'Thellungiella parvula', 'Populus trichocarpa', 'Vitis vinifera', 'Amborella trichopoda', 'Oryza sativa', 'Zea mays', 'Brachypodium distachyon', 'Spirodela polyrhiza', 'Selaginella moellendorffi', 'Physcomitrella patens', 'Chlamydomonoas reinhardtii', 'Ostreococcus lucimarinus', 'Lemna gibba', 'Posidonia australis' ,'Amphibolis antarctica', 'Wolffia australiana')
```

@@

```{r fig.width=14}
plot(ggdraw()+cowplot::draw_image('./data/species_timetree.svg'))
```

@@

```{r}
tree <- read.tree('./data/timetree_species.nwk')
```

### 2021-10-07 analysis/Orthofinder.Rmd
Missing commits
wflow_publish(files = c("analysis/*"))

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(patchwork)
library(UpSetR)
```

```{r}
groups <- read_tsv('data/Orthogroups.tsv')

names(groups) <- c('Orthogroup', 'A. antarctica', 'A. trichopada', 'B. distachyon', 'C. reinhardtii', 'L. gibba', 'O. sativa', 'P. australis', 'P. patens', 'P. trichocarpa', 'S. moellendorffii', 'S. polyrhiza', 'A. thaliana', 'T. parvula', 'V. vinifera', 'Z. mays', 'Z. muelleri', 'Z. marina', 'O. lucimarinus')
```

@@

```{r}
species_names <- per_spec %>% 
  group_by(Orthogroup) %>% 
  group_by(Orthogroup) %>% 
  summarise(catty = paste0(sort(name), collapse = ', '))
```

@@

```{r}
species_names %>% dplyr::filter(catty == 'A. antarctica, P. australis, Z. marina, Z. muelleri') %>% nrow()
```

```{r}
species_names %>% dplyr::filter(catty == 'A. antarctica, P. australis') %>% nrow()

```{r}
species_names %>% dplyr::filter(catty == 'A. antarctica, P. australis, Z. marina') %>% nrow()

```
```{r}
species_names %>% dplyr::filter(catty == 'A. antarctica, P. australis, Z. muelleri') %>% nrow()
```

```{r}
species_names %>% dplyr::filter(catty == 'P. australis, Z. marina, Z. muelleri') %>% nrow()
```

I should automate this.... and I can!

@@

This can't be right, how are 6532 clusters suddenly shared.... that's less than the overall. Need to subset the original clusters, NOT the species.

>>>>

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(patchwork)
library(UpSetR)

```{r}
groups <- read_tsv('./data/Orthogroups.tsv')

names(groups) <- c('Orthogroup', 'A. antarctica', 'A. trichopada', 'B. distachyon', 'C. reinhardtii', 'L. gibba', 'O. sativa', 'P. australis', 'P. patens', 'P. trichocarpa', 'S. moellendorffii', 'S. polyrhiza', 'A. thaliana', 'T. parvula', 'V. vinifera', 'Z. mays', 'Z. muelleri', 'Z. marina', 'O. lucimarinus', 'W. australis')
```

@@

@@

@@

### 2021-10-07 analysis/plot.Rmd
Add missing files
wflow_publish(files = list.files("analysis/", pattern = "*Rmd",     full.names = T))
wflow_publish(files = c("analysis/*"))

---
title: "Untitled"
author: "Philipp Bayer"
date: "4 March 2021"
output: html_document
---

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(patchwork)
```

@@

reps <- readxl::read_xlsx('data/Repeat_coding.xlsx')

@@

```{r}
p1 <- reps %>% ggplot(aes(x=Assembly, fill=Class, y = BP/1000000)) + 
geom_bar(position='stack', stat='identity') + ylab('Size (Mbp)') +
  scale_fill_brewer(palette='Dark2') +
  theme(axis.text.x =  element_text(face="italic"))

@@

```{r}
p2 <- reps %>% ggplot(aes(x=Assembly, fill=Class, y = Percent)) + geom_bar(position='stack', stat='identity')+
  scale_fill_brewer(palette='Dark2') +
  theme(axis.text.x =  element_text(face="italic")) +
  ylab('Percent\n of assembly')
p2
```
```{r fig.width = 10, dpi=300}
p1/p2 + plot_annotation(tag_levels = 'A')
```

>>>>

---
title: "Genomic comparison"
author: "Philipp Bayer"
date: "4 March 2021"
output: html_document
---

```{r setup}
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
library(RColorBrewer)
library(wesanderson)
library(patchwork)
```

@@

reps <- readxl::read_xlsx('./data/Repeat_coding.xlsx')

@@

```{r}
pal <- wes_palette("Zissou1", 6, type = "continuous")
p1 <- reps %>% ggplot(aes(x=Assembly, fill=Class, y = BP/1000000)) + 
geom_bar(position='stack', stat='identity') + ylab('Size (Mbp)') +
  #scale_fill_brewer(palette='Dark2') +
  scale_fill_manual(values=pal) +  
  theme(axis.text.x =  element_text(face="italic"))

@@

```{r}
p2 <- reps %>% ggplot(aes(x=Assembly, fill=Class, y = Percent)) + geom_bar(position='stack', stat='identity')+
  #scale_fill_brewer(palette='Dark2') +
    scale_fill_manual(values=pal) +  
  theme(axis.text.x =  element_text(face="italic")) +
  ylab('Percent\n of assembly')
p2
```
```{r fig.width = 10, dpi=300}
patch <- p1/p2 + plot_annotation(tag_levels = 'A')
patch[[1]] = patch[[1]] + theme(axis.text.x = element_blank(),
                                        axis.ticks.x = element_blank(),
                                        axis.title.x = element_blank() )

patch
```
